---
title: "How R you? An evening of R-tips, discussions and celebrations"
date: "18th October - Two years anniversary!"
always_allow_html: yes
output:
  github_document:
    toc: yes
    toc_depth: 3
  html_document:
    theme: cosmo
    toc: yes
    toc_depth: 3
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(magick)
library(png)
library(grid)
library(emo)
library(icon)
```


```{r echo=FALSE,message=FALSE,fig.width=2,fig.height=2,fig.align='center',cache=TRUE}
library(png)
library(grid)
img <- readPNG("./Figures/logo.png")
grid.raster(img)
```

## How R you? - Lightning talks and panel discussion 

Have you ever had the thought: "I wonder how my friend is coding!" or "How would other people code this?" or "What's their favourite R tip?". Well, this is the time to share our coding thoughts and tips! To celebrate our two years anniveRsary we would like to bring out the R diversity of our community and for this we would like YOU TO SHARE WITH US YOUR FAVOURITE BITS OF R and we are organising a PANEL DISCUSSION with past speakers and other R experts from industry and academia!

SUBMIT YOUR FAVOURITE BITS OF R HERE AND PRESENT IT ON THE NIGHT!

1. SHARE WITH US HERE https://goo.gl/forms/Aw4REPkOCG7BLhv43 an R/R Studio function or functionality; a way to build a model or to visualise your data that you use in your workflow or that simply you really like; your favourite R moment or tips from our events! You can also add something about yourself and in which field ou use R for. The format can be one slide, one R/Rmd script or anything that works for you!

2. PRESENT IT at our event in 5 minutes. This will be a great opportunity to share your R tips, ask for feedback to the audience and practice your public speaking in a friendly and non-judgemental environment! 

3. WE WILL CREATE AN R-LADIES MELBOURNE TIPS REPOSITORY. Submit something even if you think you might not be free on the night. We'd still love to combine all the R-Ladies tips in one Rmarkdown and make it available to everyone! This will showcase the diversity of our community. Here is an example of how it will look like https://github.com/R-LadiesMelbourne/2018-10-16_How-R-You. Depending on the number of submissions we will restructure the repository into themes.

4. WIN A FABULOUS PRIZE! We will drafts LUCKY WINNERS among the presenters to win an amazing prize (R earrings, bags and much more!)!!

## Panel discussion with past speakers

Following the lightning talks we will held a panel discussion featuring some of our past speakers and other R experts from industry and academia. The panel will be announced soon!
The topics of the panel will be “the user experience of R language from various fields of proficiency” and “the impact of public speaking skills while presenting R work”. You will have the opportunity to ask any question you would like!
