---
title: "Analyse Royal Tweets `r icon::fa_twitter(colour='#00aced')` - useR! 2018"
author: "Anna Quaglieri & Saskia Freytag"
date: "useR! July 2018"
always_allow_html: yes
output:
  github_document:
    toc: yes
    toc_depth: 3
  html_document:
    theme: simplex
    toc: yes
    toc_depth: 3
---

# Packages to install

```{r eval=FALSE}
install.packages("twitteR")
install.packages("wordcloud2")
install.packages("tidyverse")
install.packages("tidytext")
install.packages("knitr")
install.packages("plotly")
devtools::install_github("ropenscilabs/icon") # to insert icons
devtools::install_github("hadley/emo") # to insert emoji
```


```{r}
library(knitr)
library(magick)
library(png)
library(grid)
library(emo)
library(icon)
library(twitteR)
library(tidyverse)
```


```{r include=FALSE,echo=FALSE}
# Chunk options
knitr::opts_chunk$set(fig.width=7,echo=TRUE, fig.height=7, warning=FALSE, message=FALSE,prompt=T,tidy=T,include=TRUE,cache=TRUE,fig.align='center',fig.asp=0.50,opts.label ="squarefigure",cache = TRUE)
```



# Reference material for the following tutorial

* [Setting up the Twitter R package for text analytics](https://www.r-bloggers.com/setting-up-the-twitter-r-package-for-text-analytics/)
* [Obtaining and using access tokens](https://cran.r-project.org/web/packages/rtweet/vignettes/auth.html)
* [Text mining with R](https://www.tidytextmining.com/index.html)


* **Refer to `Social_Media_Setup_APIs.Rmd` to setup your Twitter API and connect your R session with Twitter**


# Downloading tweets with `twitteR` 

Once you have connected to twitter `r icon::fa("twitter")` and accessed your API, you are ready to download tweets. Let's try to return the 3 most recent tweets that contain the #useR2018 hashtag. 

